\documentclass{article}

\title{Josh Chua's Resume}
\author{Josh Chua}

\usepackage[legalpaper, margin=0.5in]{geometry}
\setlength\parindent{0pt}

\usepackage{titlesec}
\titleformat{\section}
            {\normalfont\large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

\pagenumbering{gobble}
\usepackage[none]{hyphenat}

\begin{document}
\centerline{\LARGE\textbf{Josh Chua}}
\smallskip
\centerline{
  joshjchua@protonmail.com \textbullet \
  joshchua.com \textbullet \
  github.com/joshchua}

\section*{Work Experience}
\textbf{Software Developer Team Lead} \hfill October 2021 --- Present\\
\textit{Epic, Verona, WI}
\begin{itemize}
\item Managed a small team of software developers and continued software development
  responsibilities on the Unified Communications team.
\item Acted as the owner for Epic's Alert Communicator functionality which
  transmits third-party patient device and nurse call alarms to Epic apps as
  notifications. I was the point person for vision, development, and issues
  for this area.
\item Led customer calls including roadmap, sales, design, and troubleshooting discussions.
\item Managed projects developed by my team to ensure quality and timely release.
\end{itemize}
\medskip

\textbf{Software Developer} \hfill June 2020 --- Present\\
\textit{Epic, Verona, WI}
\begin{itemize}
\item On Epic's Unified Communications team, I designed and developed
  enhancements and fixes for Epic's clinical\\ communciations platform, which
  includes secure texting, push notification infrastructure, and role-based
  communication.
\item Developed full-stack solutions for Epic's main clinical desktop web application
  using C\#, TypeScript, and React and for Epic's clinician-facing mobile apps, using Java,
  Kotlin, Objective-C, and Swift.
\item Mentored five developers in their first year of full-stack web and
  mobile development.
\item Acted as Unified Communications's Database Model Reviewer and reviewed
  proposals and changes to the Epic's proprietary database.
\item Performed phone screens and interviewed software developer candidates weekly.
\end{itemize}
\medskip

\textbf{Software Development Intern} \hfill November 2019 --- May 2020\\
\textit{Initech Global, Grand Rapids, MI}
\begin{itemize}
\item Integrated an internal ERP application with QuickBooks Online using Java,
  Spring, Angular, and MySQL.
\item Architected the version 2 of the internal ERP application and its migration
  from AngularJS to Angular 9.
\end{itemize}
\medskip


\textbf{Industrial Internet of Things and Data Lake Intern}
\hfill May 2019 --- November 2019\\
\textit{Steelcase, Grand Rapids, MI}
\begin{itemize}
\item Prototyped Microsoft Azure IoT Edge on a Raspberry Pi to determine
  viability as a means of collecting IIoT data at Steelcase factories.
\item Developed a real-time dashboard to visualize IIoT data using React, Redux,
  TypeScript, and Azure SDKs.
\item Led a group project for an intern hackathon and mentored teammates in
  learning Git, C\#, React, and SQL.
\item Assisted in the migration of pieces of the Data Lake infrastructure from
  Microsoft Azure to Snowflake.
\end{itemize}
\medskip


\textbf{Desktop Support Student Technician} \hfill October 2017 --- May 2019\\
\textit{Grand Valley State University, Grand Rapids, MI}
\begin{itemize}
\item Troubleshooted computer hardware and software issues for university faculty.
\item Scheduled appointments to install new equipment or fix issues.
\end{itemize}
\medskip

\textbf{Software Development Intern} \hfill December 2018 --- March 2019\\
\textit{BDO USA, Grand Rapids, MI}
\begin{itemize}
\item Created a user provisioning screen for an existing .NET MVC web application.
\item Fixed issues with an .NET and Angular application that was developed by a
  third party vendor.
\end{itemize}
\medskip


\section*{Education}
\textbf{Bachelor of Science in Computer Science} \hfill August 2016 --- May 2020\\
\textit{Grand Valley State University, Grand Rapids, MI}

\section*{Skills}
\begin{itemize}
\item \textbf{Programing Languages}: Python, Go, C++, C\#, Java, Kotlin, Objective-C, Swift, JavaScript, TypeScript
\item \textbf{Web Development}: React, Angular, .NET MVC, Node.js
\item \textbf{Mobile Development}: Android, iOS (UIKit, SwiftUI), React Native
\end{itemize}
\end{document}
