\documentclass{article}

\title{Josh Chua's Resume}
\author{Josh Chua}

\usepackage[letterpaper, margin=0.5in]{geometry}
\setlength\parindent{0pt}

\usepackage{titlesec}
\titleformat{\section}
            {\normalfont\large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

\pagenumbering{gobble}
\usepackage[none]{hyphenat}

\usepackage{subfiles}

\begin{document}
\centerline{\LARGE\textbf{Josh Chua}}
\smallskip
\centerline{
  \ifdefined\fulldetails
  \subfile{contact.tex}
  \fi
  joshjchua@protonmail.com \textbullet \
  joshchua.com \textbullet \
  github.com/joshchua}

\section*{Work Experience}
\textbf{Software Developer Team Lead} \hfill October 2021 --- Present\\
\textit{Epic, Verona, WI}
\begin{itemize}
\item Supervised a team of software developers and continued software design and
  computer programming responsibilities.
\ifdefined\msftfocused
\else
\item Managed team development projects to ensure high quality and timely releases.
\fi
\item Oversaw Epic's Alert Communicator functionality, which transmits third-party
  patient device and nurse call alarms to Epic apps as notifications. I was the point
  person for vision, development, and issues for this area.
\ifdefined\msftfocused
\else
\item Presented to customer executives and analysts through roadmap, sales, and
  design calls.
\fi
\item Influenced key projects and unified cross-team efforts in the clinical
  communications experience space.
\end{itemize}
\medskip

\textbf{Software Developer} \hfill June 2020 --- Present\\
\textit{Epic, Verona, WI}
\begin{itemize}
\item Designed and developed enhancements and fixes for Epic's clinical communications platform, which
  includes secure text messaging, push notification infrastructure, and role-based communication.
\item Implemented full-stack solutions for Epic's clinical desktop web application
  (C\#, TypeScript, and React) and for Epic's clinician-facing mobile apps (Java,
  Kotlin, Objective-C, and Swift).
\item Mentored six developers in their first year of full-stack web and
  mobile development.
\ifdefined\msftfocused
\else
\item Ensured performance through review of proposals and changes to Epic's proprietary database
  that affected team-owned data structures as the team's Database Model Reviewer.
\item Helped HR with recruiting and interviewed software developer candidates weekly.
\fi
\end{itemize}
\medskip

\textbf{Software Development Intern} \hfill November 2019 --- May 2020\\
\textit{Initech Global, Grand Rapids, MI}
\medskip


\textbf{Industrial Internet of Things and Data Lake Intern}
\hfill May 2019 --- November 2019\\
\textit{Steelcase, Grand Rapids, MI}
\ifdefined\msftfocused
\begin{itemize}
\item Prototyped Azure IoT Edge on a Raspberry Pi to demonstrate potential use to collect telemetry data from factory machines. 
\item Developed a real-time web dashboard to view IIoT data by utilizing React, Redux, GraphQL, Node, Docker, and Azure SDKs. 
\item Led a web app project for an intern hackathon and helped teammates learn topics new to them, such as Git, .NET Core, Entity Framework Core, React, Bootstrap, Azure SQL Server, CI/CD, and Azure DevOps. 
\end{itemize}
\fi
\medskip


\textbf{Desktop Support Technician} \hfill October 2017 --- May 2019\\
\textit{Grand Valley State University, Grand Rapids, MI}
\medskip

\textbf{Software Development Intern} \hfill December 2018 --- March 2019\\
\textit{BDO USA, LPP, Grand Rapids, MI}
\ifdefined\msftfocused
\begin{itemize}
\item Implemented a user provisioning screen on an internal .NET MVC web application through integration with Active Directory.
\item Debugged and fixed critical issues on an initially unusable .NET and Angular project that was purchased from a third party vendor.
\end{itemize}
\fi
\medskip


\section*{Education}
\textbf{Bachelor of Science in Computer Science} \hfill August 2016 --- May 2020\\
\textit{Grand Valley State University, Allendale, MI}
\begin{itemize}
\item Minor in General Business
\end{itemize}
\section*{Skills}
\begin{itemize}
\item \textbf{Programing Languages}: Python, C, C++, Go, C\#, Java, Kotlin, Objective-C, Swift, JavaScript, TypeScript
\item \textbf{Web Development}: React, Angular, .NET MVC, Spring, Node.js
\item \textbf{Mobile Development}: Android, iOS (UIKit, SwiftUI), React Native
\item \textbf{Other}: Git, Subversion (SVN), SQL, Microsoft Azure, Amazon Web Services (AWS)
\end{itemize}
\end{document}
